Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-01 cvpr2018.tex
backup

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we omit the batch index and summarize the algorithm using SGD for simplicity.}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]
 		\For{$i \gets 1 \textrm{ to } S$ }
 		\For{$k \gets 1 \textrm{ to } ncritic$}
 		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
 		\State Sample one matching image text pair $\{x, t\}$ and mismatched one $\{x, \hat{t}\}$.
 		\State Generate fake image samples for both $t$ and $\hat{t}$
 		\begin{equation}
 		\begin{split}
	 		& {o} = G(t, z_1) \\
	 		& {\hat{o}} = G(\hat{t}, z_2) 
 		\end{split}
 		\end{equation}
	 		\For{each discriminator $D_i$ }
		 		\State Update $D_i$ by descending the gradient of loss \ref{equ:totalD}:
		 		\begin{equation}
		 		   	\theta_{D_i} = \theta_{D_i}  - \nabla_{\theta_{D_i}} \mathcal{L}_d(D_i, X_i,o_i,\hat{o_i}, t,\hat{t})
		 		\end{equation}
	 		\EndFor
 		\EndFor
 		\State Update the generator by descending it's stochastic gradient of loss \ref{equ:totalG}:
 		\begin{equation}
 		\theta_{G} = \theta_{G}  - \nabla_{\theta_{G}} \mathcal{L}_g(G, o, \hat{o}, t)
 		\end{equation}

@@

\subsection{Implementation Details}
A algorithm that summarizes the training process of our model is given in Algorithm 1. We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4. We decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO. We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset. Adam optimizer is used for all experiments.
The number of repeat residual blocks is set to 1 for CUB and Oxford, 2 for COCO. We use batch size 16 for all experiments.

>>>>

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we omit the batch index and summarize the algorithm using SGD for simplicity.}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]
 		\For{$i \gets 1 \textrm{ to } S$ }
 		\For{$k \gets 1 \textrm{ to } ncritic$}
 		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
 		\State Sample one batch of matching and mismatching image text pair $\{X, t\}$,  $\{X, \hat{t}\}$.
 		\State Generate fake image samples for both $t$ and $\hat{t}$
 		\begin{equation}
 		\begin{split}
	 		& {o} = G(t, z_1) \\
	 		& {\hat{o}} = G(\hat{t}, z_2) 
 		\end{split}
 		\end{equation}
	 		\For{each discriminator $D_i$ }
		 		\State Update $D_i$ by descending the gradient of loss \ref{equ:totalD}:
		 		\begin{equation}
		 		   	\theta_{D_i} = \theta_{D_i}  - \nabla_{\theta_{D_i}} \mathcal{L}_d(D_i, X_i,o_i,\hat{o_i}, t,\hat{t})
		 		\end{equation}
	 		\EndFor
 		\EndFor
 		\State Update the generator by descending it's stochastic gradient of loss \ref{equ:totalG}:
 		\begin{equation}
 		\theta_{G} = \theta_{G}  - \nabla_{\theta_{G}} \mathcal{L}_g(G, o, \hat{o}, t)
 		\end{equation}

@@

\subsection{Implementation Details}
A algorithm that summarizes the training process of our model is given in Algorithm 1. We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4. We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset. Adam optimizer with momentum 0.5 is used for all experiments.  The initial learning rate is set as 0.0002 and we decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO.
The number of repeat residual blocks is set to 1 for CUB and Oxford, 2 for COCO. We use batch size 16 for all experiments.
